Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-07-10 manuscript/main.tex
remove different evaluation point notation

	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}
 Thus, each observation is represented by a finite-dimensional vector $X_i^{(k)}(\mathbf{t}_k) \in \mathbb{R}^{|\mathbf{t}_k|}$, where $\mathbf{t}_k \subset \mathcal{T}_k$.

Given an orthonormal basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
\begin{equation*}
	X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t), \quad 
	\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t),
\end{equation*}
where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
In practice, functional predictors are observed only at a finite set of time points rather than as complete curves. Rather than reconstructing infinite-dimensional object stated above via finite observations, we approximate each predictor using a finite-dimensional projection by truncating its basis expansion at a finite number $M$. This $M$ can be set to a sufficiently large value (e.g., 15 or 20) to capture a wide range of functional patterns. 
Notably, it is unnecessary to fine-tune $M$, as a  penalization scheme introduced in Section \ref{sec: Regularization of PLS Components} regularizes each functional component to achieve the desired smoothness. We denote the projected predictors and coefficients as
\begin{equation*}
	\widetilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
	\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
\end{equation*}
The $i$th  hybrid predictor with projected functional parts, is a tuple, denoted as
\begin{equation*}
	\widetilde{W}_i := 
	(
	X_{i1}, \ldots, X_{iK}, \boldsymbol{Z}_i
	).
\end{equation*}
We adopt the following notion for the coefficients:
\begin{equation}
	 \boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top \in \mathbb{R}^M,
	 \quad
	 \boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top  \in \mathbb{R}^M,
\end{equation}
and
\begin{equation}
	 \Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
\end{equation}

@@

	\bibliographystyle{apa} 
	\bibliography{Reference}

>>>>

	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}	
	Given an orthonormal basis $\{b_l(t)\}$ of $L^2([0,1])$, the functional predictors and the corresponding regression coefficients can be decomposed into
	\begin{equation*}
		X_{ij}(t) = \sum_{l=1}^\infty \theta_{ijl} \, b_l(t), \quad 
		\beta_j(t) = \sum_{l=1}^\infty \eta_{0,jl} \, b_l(t),
	\end{equation*}
	where $\theta_{ijl}$ and $\eta_{0,jl}$ are the coefficients of $X_{ij}(t)$ and $\beta_j(t)$ corresponding to the $l$th basis function $b_l(t)$, respectively.
	In practice, functional predictors are observed only at a finite set of time points rather than as complete curves. Rather than reconstructing infinite-dimensional object stated above via finite observations, we approximate each predictor using a finite-dimensional projection by truncating its basis expansion at a finite number $M$. This $M$ can be set to a sufficiently large value (e.g., 15 or 20) to capture a wide range of functional patterns. 
	Notably, it is unnecessary to fine-tune $M$, as a  penalization scheme introduced in Section \ref{sec: Regularization of PLS Components} regularizes each functional component to achieve the desired smoothness. We denote the projected predictors and coefficients as
	\begin{equation*}
		\widetilde{X}_{ij}(t) = \sum_{l=1}^M \theta_{ijl} \, b_l(t), \quad 
		\tilde{\beta}_j(t) = \sum_{l=1}^M \eta_{0,jl} \, b_l(t).
	\end{equation*}
	The $i$th  hybrid predictor with projected functional parts, is a tuple, denoted as
	\begin{equation*}
		\widetilde{W}_i := 
		(
		X_{i1}, \ldots, X_{iK}, \boldsymbol{Z}_i
		).
	\end{equation*}
	We adopt the following notion for the coefficients:
	\begin{equation}
		\boldsymbol{\theta}_{ij} := (\theta_{ij1}, \ldots, \theta_{ijM})^\top \in \mathbb{R}^M,
		\quad
		\boldsymbol{\eta}_{0j} := (\eta_{0,j1}, \ldots, \eta_{0,jM})^\top  \in \mathbb{R}^M,
	\end{equation}
	and
	\begin{equation}
		\Theta_j := (\boldsymbol{\theta}_{1j}, \ldots, \boldsymbol{\theta}_{nj})^\top  \in \mathbb{R}^{n \times M}.
	\end{equation}

@@
